---
title: "Enhancing Variable Labels in Regression Models with labelstar"
author: "Louis-Jonas Heizlsperger"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Enhancing Variable Labels in Regression Models with labelstar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

## Introduction

The `labelstar` package provides tools to enhance your regression models with descriptive variable labels. This vignette demonstrates how to use `labelstar` to apply custom labels to variables and integrate these labels into regression output using the `stargazer` package.

## Installation

First, install the `labelstar` package from GitHub:

```{r setup, results = "hide", message = FALSE, warning = FALSE}
devtools::install_github('https://github.com/louisheizlsperger/labelstar')
library(labelstar)
```

## Load the Data

We will use the `diamonds` dataset included in `ggplot2` as an example, and define custom labels for it.

```{r load-data}
# Load ggplot2 package for example dataset
library(ggplot2)

# Define custom variable labels
variable_labels <- list(
  price = "Price (in US dollars)",
  carat = "Weight",
  cut = "Quality of the cut",
  color = "Color",
  clarity = "Clarity ",
  x = "Length (in mm)",
  y = "Width (in mm)",
  z = "Depth (in mm)",
  depth = "Total depth percentage",
  table = "Width of top relative to widest point"
)
```

## Basic Usage
Apply the labels to the dataset and demonstrate basic usage with a simple regression model.

```{r ols-spec, results = "hide", message = FALSE, warning = FALSE}
library(stargazer)

# Apply the labels to the dataset
diamonds <- labelstar::assign_labels(diamonds, variable_labels)

# Example formula
formula_basic <- as.formula("price ~ carat + depth")

# Get variable labels using the new function
labels <- labelstar::get_labels(formula_basic, diamonds)

# Run regression
model <- lm(formula_basic, data = diamonds)
```

Now we create the ```stargazer``` table with our custom labels.

```{r ols-table, results = "asis"}
# Display the regression results with labeled variables
stargazer(model, 
          type = 'html', 
          # Variable labels
          dep.var.labels = labels$dep_var_label, 
          covariate.labels = labels$covariate_labels,
          # Additional table details
          notes.append = FALSE,
          notes = labels$table_notes)
```

## More Advanced Usage
Extend the example to include more covariates and fixed effects using the lfe package.

```{r fe-spec}
library(lfe)

# Update formula to include more covariates
formula_fe <- as.formula("price ~ carat + depth + carat*depth | cut + color | 0 | cut")

# Get updated labels using the new function
labels <- labelstar::get_labels(formula_fe, diamonds)

# Run a more regression model with fixed effects
model <- lfe::felm(formula_fe, data = diamonds)
```

Again, we create the ```stargazer``` table using custom labels.

```{r fe-table, results = "asis"}
# Display the regression results with labeled variables
stargazer(model, 
          type = 'html', 
          # Variable labels
          dep.var.labels = labels$dep_var_label,
          covariate.labels = labels$covariate_labels,
          # Additional table details
          add.lines = labels$fe_labels,
          notes.append = FALSE,
          notes = labels$table_notes)
```

## Conclusion
The ```labelstar``` package provides a convenient way to apply descriptive labels to variables in your datasets and ensures these labels are reflected in your regression outputs. This enhances the readability and interpretability of your statistical analyses.
